### 2024-08-15 Scripts/Manuscript/manuscript.Rmd
minor code and text fixes

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"

@@

abstract: |
  Recent studies have shown that challenges in measurement practices may have contributed to the “replication crisis” in psychological science. 
  However, the nature and extent of the association between measurement and replicability remains unclear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability. 
  Results from logistic regressions indicated that questionable practices in reporting on measurement (QMPs) in replication studies (b = -5.60, p = .006), but not its reliability (b = 8.21, p =. 106) was associated with lower replicability. <!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.--> 
  Furthermore, Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
  We additionally found that reliability and validity evidence was rarely reported. 
  These findings corroborate existing research that construct validity in published research is low and that may have negative consequences for replications. 
  We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.

keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
wordcount         : "159"

@@

# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
r_refs("r-references.bib")

# manually retrieving the Rstudio version
rstudioapi::versionInfo()

@@

Measurement reliability varies across samples. Therefore, we investigated what the reliability is in replications of psychological research (RQ1a) and original psychological research (RQ1b).

The Many Labs studies were intended as direct replications. In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability]. As a result, we expected that there would be, no difference present in the reliability between replication research and original psychological research (H1).

Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring]. We thus investigated whether reliability estimates differed between replicating labs (RQ2).

Heterogeneity in reliability may be contributing strongly to the variation in reliability between labs. However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expected that there would be no significant variation in the reliability estimates of replications of the same original study (H2) as well.

To see if reliability is related to replication success, we investigated whether there is an association between successfully replicated study reliability and replication outcome (RQ3).

Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance. THus, we expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).

@@

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because of the use of structured protocols documenting the measurement.

QMPs obscure information relevant to mimic measurement from original research in subsequent replication attempts. The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct]. Thus we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).

@@

QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts. We investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).

@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research. @shaw2020measurement already found such a spill-over effect for validity. In line with this research we expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was being replicated. Multiple psychological constructs could be measured per original study or replication. We used the the replication protocols to identify these measures. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.

@@

We retrieved the data on the replication protocols, and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document).

@@

We developed and used a coding protocol (the [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) is available in the supplementary materials) to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies.

@@

# adding a superscript for a later footnote
replication_nr_table$"Nr. Replicated"[3] <- "$3^a$"

# print the table in apa formatting
apa_table(
  replication_nr_table, align = c("l", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "Nr. measures refers to the total number of primary measures extracted, while Nr. replicated displays the number of measures for which the associated effect was replicated successfully. $^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated. These have been treated as not replicated within this table and in further analyses throughout the article. "
  , escape = FALSE, placement = "htp", midrules = 4)

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^2]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

[^1]: Initially the original articles contained 3 more measures than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.

[^2]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)). We found that removing these measures' data had minimal impact on the overall results. Therefore, the results presented below were based on data from all the measures.

@@

### Hypothesis 1: Reliability Reporting in Original Compared to Replication Research.

@@

### Hypotheis 2: Within Study Variation in Reliability.

@@

We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.

@@

Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`). Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).

@@

# first we calculate the odds-ratio
OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 2)

@@

# and then convert them to odds ratio CIs
OR_CI_LOW <- round(exp(log_OR_CI_LOW), 2)
OR_CI_HI <- round(exp(log_OR_CI_HI), 2)

@@

We additionally pre-registered a random intercept and random-slope multilevel regression model of the same relationship with each lab's unique reliability nested within the set of replication of an effect. However, because our dependent variable (replicability) is at the group level, we decided based on suggestions in the literature [@foster-johnson2018Predicting] to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency. This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`). However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.

@@

# recycled H1 test
# A chi square test for difference in N reliability reported for multiple 
# item measures.
reliability_reporting_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])

@@

Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did. Furthermore, we conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis. We found that `r sum(cfa_results$Single_factor == "Yes")` of these measures met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^3].

[^3]: As of writing this article the *betareg* package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.

@@

We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between types (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).

@@

The underreporting of reliability and validity evidence has long been discussed [@willson1980research;@vacha1999practices; @green2011recent]. Our study illustrates three potential reasons for why this problem has persisted. Firstly, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement. Calculating reliability for single-item measures is not as straightforward and less common as for multiple item measures [@wanous1996estimating]. Concerns with the use of single-item measures go beyond reliability, validity may also be at risk. Single-item measures because they are singular come with an assumption of unidimensionality regarding the construct they, which our exploratory analyses revealed is an assumption that did not frequently hold for multiple-item measures in our sample. However, we did not explore validity concerns unrelated to reporting in-depth, therefore future research is needed to determine the extent of problems with validity.

@@

In line with Hypotheses 5 & 6, we found an indication of such a spillover effect in our sample. The total QMPs of an original study and the total QMPs in the protocol of the replication for the same study were positively associated. Furthermore, we found that QMPs may have negatively impacted replicability. An increase in total QMP ratio was associated with a decrease in replicability. These associations together indicate that poor measurement reporting in an original study could be a risk factor for subsequent replication attempts.

However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for results based on the initial protocol). Furthermore, these Hypotheses were supported by only one of the multilevel models. However, these models were limited in group and sample size making their interpretation precarious.

@@

Our study had several limitations. We encountered numerous challenges in operationalizing QMPs. Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an operationalization to assess measurement practices and evaluate their impact on replicability. However, this also means that it remains uncertain if our operationalization accurately captured the concept. We encountered particular difficulty in determining when a practice is questionable, and the impact of the context on this decision. As a result, we already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol. This revision was not trivial, as it altered the interpretation of our results. This finding reflects the challenges we encountered in operationalizing QMPs in a single index.

Another challenge in constructing a QMP variable was the way to treat practices that were not applicable to a particular measurement. We chose to construct ratios to cancel out the effects of non-applicable items as much as possible. However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero. Yet, we would not consider the latter case to indicate the same level of completeness as the first. A little more than one third of all responses were not applicable. As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent.

@@

A fourth limitation is that we of only used one definition of replication success. Replication success can be estimated and framed in multiple ways [for an example in replication research, see @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error. The relationship between reliability and other indices of replication success may differ.

>>>>

author: 
  - name          : "Goos, Cas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"

@@

abstract: |
  Recent studies have shown that challenges in measurement practices may have contributed to the “replication crisis” in psychological science. 
  However, the nature and extent of the association between measurement and replicability remains unclear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability. 
  Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
  We additionally found that reliability and validity evidence was rarely reported. 
  Furthermore, logistic regression results indicated that "questionable measurement practices" (QMPs) in replication studies were associated with lower replicability (b = -5.60, p = .006), while study reliability was not (b = 8.21, p =. 106) . <!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.--> 
  These findings corroborate existing research that construct validity in published research is unknown, which may have negative consequences for replications. 
  We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
wordcount         : "166"

@@

# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
r_refs("r-references.bib")
```

@@

Measurement reliability varies across samples. Accounting for the differences between original and replication is crucial for evaluating replications. This includes variation in measurement reliability. Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b). The Many Labs studies were intended as direct replications, which implies that any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability]. Therefore, we expected that there would be, no difference in reliability between replication research and original research (Hypothesis 1; H1).

[^1]: The numbering of the research questions and hypotheses matches the numbering in the preregistration

Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring]. We empirically investigated this in our sample by investigating whether reliability estimates differed between replicating labs (RQ2). For effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expect that there is no significant variation in the reliability estimates of replications of the same original study (H2) either.

In theory, there should be a positive relation between reliability and replicability. Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance. To empirically assess this, we investigated whether there is an association between replication study reliability and replication outcome (RQ3). We expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).

@@

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because othe Many :abs replications used structured protocols documenting the measurement.

QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts. The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct]. Therefore, we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).

@@

@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research. @shaw2020measurement already found such a spill-over effect for validity. In line with this research we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6). We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was being replicated. Multiple psychological constructs could be measured per original study or replication. We used the replication protocols to identify these measures. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.

@@

We retrieved the data on the replication protocols, and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) in the supplementary materials.

@@

To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

We developed a [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) (available in the supplementary materials; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) to extract information on the reported measurements for both replication protocols and original studies.

@@

# adding replication ratio's to the Nr. Replicated column
replication_ratio <- apa_num(replication_nr_table$"Nr. Replicated" / replication_nr_table$"Nr. Measures", gt1 = FALSE)

replication_nr_table$"Nr. Replicated"[c(1, 2, 4, 5)] <- paste(replication_nr_table$"Nr. Replicated"[c(1, 2, 4, 5)], paste0("(", replication_ratio[c(1, 2, 4, 5)], ")"))

# adding a superscript for a later footnote
replication_nr_table$"Nr. Replicated"[3] <- paste(paste0(replication_nr_table$"Nr. Replicated"[3], "$^a$"), paste0("(", replication_ratio[3], ")"))

# print the table in apa formatting
apa_table(
  replication_nr_table, align = c("l", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "Nr. measures refers to the total number of primary measures extracted, while Nr. replicated displays the number of measures for which the associated effect was replicated successfully. The value between brackets represent the ratio of replications. $^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated. These have been treated as not replicated within this table and in further analyses throughout the article. "
  , escape = FALSE, placement = "htp", midrules = 4)

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^3]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

[^2]: Initially the original articles contained 3 more measures than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.

[^3]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)). We found that removing these measures' data had minimal impact on the overall results. Therefore, the results presented below were based on data from all the measures.

@@

### Hypothesis 1: Reliability Reporting in Original and Replication Research.

@@

### Hypothesis 2: Within Study Variation in Reliability.

@@

@@

We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures. Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`). Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).

@@

# first we calculate the odds-ratio
OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 1)

@@

# and then convert them to odds ratio CIs
OR_CI_LOW <- round(exp(log_OR_CI_LOW), 1)
OR_CI_HI <- round(exp(log_OR_CI_HI), 1)

@@

We additionally pre-registered a random intercept and random-slope multilevel regression model of the same relationship with each lab's unique reliability nested within the set of replication of an effect. However, because our dependent variable (replicability) is at the group level, we decided to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency [as suggested by @foster-johnson2018Predicting]. This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`). However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.

@@

# recycled H1 tests
# A chi square test for difference in N reliability reported for multiple 
# item measures.
reliability_reporting_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])

# whether there was evidence from a factor analysis 
factor_present <- c(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")

# A chi square test for difference in N factor analysis evidence reported for multiple 
# item measures.
factor_reporting_test_result <- chisq.test(data_h1$rep_org, factor_present)

@@

Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. Validity evidence from a factor analysis was reported in `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications. This difference was not significant, however the total number of factor analyses reported were few ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).

To gain a better understanding of the validity of the included measurements, we also conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis. We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity. We found that `r sum(cfa_results$Single_factor == "Yes")` of these measures met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^4].

[^4]: The *betareg* package currently does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.

@@

We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between the separate QMP types and replicability (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).

@@

The underreporting of reliability and validity evidence has long been discussed [@willson1980research;@vacha1999practices; @green2011recent]. Our study illustrates three potential reasons for why this problem has persisted. Firstly, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement. Calculating reliability for single-item measures is less straightforward and common than for multiple item measures [@wanous1996estimating]. Concerns with the use of single-item measures go beyond reliability, validity may also be at risk. Single-item measures because they are singular come with an assumption of unidimensionality regarding the construct they, which our exploratory analyses revealed is an assumption that did not frequently hold for multiple-item measures in our sample. However, we did not explore validity concerns unrelated to reporting in-depth, therefore future research is needed to determine the extent of problems with validity.

@@

In line with Hypotheses 5 & 6, we found an indication of such a spillover effect in our sample. The total QMPs of an original study and the total QMPs in the protocol of the replication for the same study were positively associated. Furthermore, we found that QMPs may have negatively impacted replicability. An increase in total QMP ratio was associated with a decrease in replicability. These associations together indicate that poor measurement reporting in an original study could be a risk factor for subsequent replication attempts. We did observe that unidimensionality was not universal among the measures for which we could run a factor analysis, which assuming that the measures were meant to be unidimensional would indicate that measures may not have assessed their construct as they were intended to.

However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for results based on the initial protocol). Furthermore, these hypotheses were supported by only one of the multilevel models. However, these models were limited in group and sample size making their interpretation uncertain.

@@

Our study had several limitations. We encountered several challenges in operationalizing QMPs. Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an operationalization to assess measurement practices and evaluate their impact on replicability. However, this also means that it remains uncertain if our operationalization accurately captured the concept. We encountered particular difficulty in determining when a practice is questionable, and the impact of the context on this decision. As a result, we already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol. This revision was not trivial, as it altered the interpretation of our results. This finding reflects the challenges in operationalizing QMPs in a single index.

Another challenge in constructing one overarching QMP variable was the way to treat practices that were not applicable to a particular measurement. We chose to construct ratios to cancel out the effects of non-applicable items as much as possible. However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero. Yet, we would not consider the latter case to indicate the same level of completeness as the first. A little more than one third of all responses were not applicable. As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent.

@@

A fourth limitation is that we used only one definition of replication success. Replication success can be estimated and framed in multiple ways [for an example in replication research, see @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error. The relationship between reliability and other indices of replication success may differ.

### 2024-08-15 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
minor code and text fixes

@@

```{r OriginalQMPDIfference}
# comparing the mean and sd replication QMP ratio 
print(c("mean decreased" = mean(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),

>>>>

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(sandwich)
library(lmtest)

# loading source script
source(file = "../../Scripts/source_script.R")

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
load_data() 
```

@@

```{r ReplicationQMPDIfference}
# comparing the mean and sd replication QMP ratio 
print(c("mean decreased" = mean(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
